---
title: "README"
output: 
  html_document:
    keep_md: yes
    highlight: tango
author: "Marcus W. Beck, beck.marcus@epa.gov"
---

### Files

All data files created from raw data in `ignore` folder using `R\dat_proc.R`

`dum.RData` Dumbarton time series data from `Dumbarton_07022013_04282016_L1.csv`

`dum_evalcor.RData` ggplot of tidal/sun correlations at Dumbarton

`new.RData` Newark time series data from `Newark_04212015_05132016_L1 (1).csv`

`new_evalcor.RData` ggplot of tidal/sun correlations at Newark

```{r echo = F, message = F, cache = F}
library(SWMPr)
library(dplyr)
library(tidyr)
library(WtRegDO)
source('R/funcs.R')
```

### Correlation between sun angle and tidal change at each site

Dumbarton

```{r echo = F, message = F, fig.height = 3, fig.width = 8}
data(dum_evalcor)
dum_evalcor + scale_y_continuous(limits = c(-0.4, 0.4))
```

Newark

```{r echo = F, message = F, fig.height = 3, fig.width = 8}
data(new_evalcor)
new_evalcor + scale_y_continuous(limits = c(-0.4, 0.4))
```
